---
title: "Mini-Project 2"
author: "Yi Wang & Ziwei 'Crystal' Zang"
date: "March 24, 2017"
output: html_document
---


## Loading the data


```{r, include=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

```{r}
library(dplyr)
library(ggplot2)
```

## function, join, 5 verbs,  Issues tab, blog post text

##Rename
```{r}
committees_copy <- committees%>%
  rename(cand_pcc = cmte_id)
```

##Contribution in a closer look
```{r}
transaction_cand <- contributions%>%
  group_by(cand_id)%>%
  summarize(N = n(), transaction_amountsum = sum(transaction_amt))
  
```

##Join each candidate id with its corresponding contribution committees
```{r}
house_win<-house_elections%>%
  #Only looking at the candidates win the house election
  filter(ge_winner=="W")%>%
  rename(cand_id = fec_id)%>%
  #Looking at the detail information of each candidate
  left_join(candidates, by = "cand_id")%>%
  #also add their committees info for next step analysis
  left_join(committees_copy, by = "cand_pcc")%>%
  #rename the column for join
  rename(cand_id = cand_id.x)%>%
  #add transaction amount into our table for future analysis
  left_join(transaction_cand, by = "cand_id")%>%
  #omit unnessary data
  select(cand_id,candidate_name,party, general_votes, cand_election_yr,cand_office_state, cand_pcc, cmte_name, transaction_amountsum)
```

```{r}
contributions%>%
  group_by(cand_id)%>%
  summarise(sum=sum(transaction_amt))
```

### scatterplot - is there a relation between votes and money?

```{r}
ggplot(house_win,aes(x=log(transaction_amountsum),y=log(general_votes), col=party))+geom_jitter()
```


### does this pattern holds for both parties?
```{r}
ggplot(subset(house_win,party %in% c("D","R")) ,aes(x=log(transaction_amountsum),y=log(general_votes)))+geom_jitter()+facet_grid(.~factor(party))+stat_smooth(method="lm", se=F)
                                                                                                      

```

### linear model - prove a statistically significant correlation

we fit a linear model to prove the theory. As we can see from a very low p-value. We can carefully suggest that there is a correlation between transaction amount and general votes of winning candidates. 

```{r}
fit <- lm( general_votes~ transaction_amountsum , data=house_win)
summary(fit)
```


### does this pattern holds for both parties?
```{r}
ggplot(subset(house_win,party %in% c("D","R")) ,aes(x=log(transaction_amountsum),y=log(general_votes)))+geom_jitter()+facet_grid(.~factor(party))+stat_smooth(method="lm", se=F)
                                                                                                      
```

As we can see from facet grid, for Democrats, as transaction amount goes up, votes increases with it while surprisingly, for Rebulican, it seems to work the opposite way. (WWOWW)
