---
title: "Mini-Project 2"
author: "Yi Wang & Ziwei 'Crystal' Zang"
date: "March 24, 2017"
output: html_document
---


## Loading the data


```{r, include=FALSE}
load("house_elections.rda")
load("candidates.rda")
load("committees.rda")
load("contributions.rda")
```

```{r}
library(dplyr)
library(ggplot2)
```

## function, join, 5 verbs,  Issues tab, blog post text

##Rename
```{r}
committees_copy <- committees%>%
  rename(cand_pcc = cmte_id)
```

##Contribution in a closer look
```{r}
transaction_cand <- contributions%>%
  group_by(cand_id)%>%
  summarize(N = n(), transaction_amountsum = sum(transaction_amt))
  
```

##Join each candidate id with its corresponding contribution committees
```{r}
house_win<-house_elections%>%
  #Only looking at the candidates win the house election
  filter(ge_winner=="W")%>%
  rename(cand_id = fec_id)%>%
  #Looking at the detail information of each candidate
  left_join(candidates, by = "cand_id")%>%
  #also add their committees info for next step analysis
  left_join(committees_copy, by = "cand_pcc")%>%
  #rename the column for join
  rename(cand_id = cand_id.x)%>%
  #add transaction amount into our table for future analysis
  left_join(transaction_cand, by = "cand_id")%>%
  #omit unnessary data
  select(cand_id,candidate_name,party, general_votes, cand_election_yr,cand_office_state, cand_pcc, cmte_name, transaction_amountsum)
```

```{r}
contributions%>%
  group_by(cand_id)%>%
  summarise(sum=sum(transaction_amt))
```

<<<<<<< HEAD
### scatterplot - is there a relation between votes and money?

```{r}
ggplot(house_win,aes(x=log(transaction_amountsum),y=log(general_votes), col=party))+geom_jitter()
```


### does this pattern holds for both parties?
```{r}
ggplot(subset(house_win,party %in% c("D","R")) ,aes(x=log(transaction_amountsum),y=log(general_votes)))+geom_jitter()+facet_grid(.~factor(party))+stat_smooth(method="lm", se=F)
                                                                                                      

=======
##Function for transaction amount for winning house candidates per states
```{r}
transaction_per_state <- function(state_arg){
  house_win%>%
    select(cand_office_state, transaction_amountsum)%>%
    group_by(cand_office_state)%>%
    summarise(transactionsum = sum(transaction_amountsum))%>%
    filter(cand_office_state == state_arg)
}
##Transaction Sum for State MA's and VA's winning house candidates, by running this function, the transaction sum for each state without writing repeatative commands
transaction_per_state(state_arg = "MA")
transaction_per_state(state_arg = "VA")
>>>>>>> 363acca5501ef4c2f0d0f15b6257c605d0fd7316
```

### linear model - prove a statistically significant correlation

we fit a linear model to prove the theory. As we can see from a very low p-value. We can carefully suggest that there is a correlation between transaction amount and general votes of winning candidates. 

```{r}
fit <- lm( general_votes~ transaction_amountsum , data=house_win)
summary(fit)
```


### does this pattern holds for both parties?
```{r}
ggplot(subset(house_win,party %in% c("D","R")) ,aes(x=log(transaction_amountsum),y=log(general_votes)))+geom_jitter()+facet_grid(.~factor(party))+stat_smooth(method="lm", se=F)
                                                                                                      
```

<<<<<<< HEAD
As we can see from facet grid, for Democrats, as transaction amount goes up, votes increases with it while surprisingly, for Rebulican, it seems to work the opposite way. (WWOWW)
=======



>>>>>>> 363acca5501ef4c2f0d0f15b6257c605d0fd7316
